---
title: "case_study"
author: "Lorraine Kwok"
date: "October 8, 2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## case study

```{r}
library(p8105.datasets)
data("nyc_airbnb")
```

## Questions 

* how are airbnb prices related to rent in the neighborhood?
* which neighborhood is most expensive and which is cheapest? 
* do hosts with multiple sites have higher prices or ratings?
* does price have any relation to ratings? 
* is average length of stay related to neighborhood? price? etc? 

## Does price have any relation to ratings?

```{r}
nyc_airbnb_price_rate = 
  nyc_airbnb %>%
  mutate(.data = ., 
         stars = review_scores_location/2,
         borough = neighbourhood_group, 
         borough = as.factor(borough)) %>%
  drop_na(dat = ., review_scores_location) %>%
  select(.data = ., id, price, stars, number_of_reviews, name, borough, neighbourhood, room_type) %>%
  ggplot(aes(x = price, y = review)) + 
  geom_point()
```

* Determining median price of airbnb rentals across the boroughs 
```{r}
#nyc_airbnb %>%
#  group_by(neighbourhood_group) %>%
#  summarize(med_price = median(price, na.rm = TRUE)) %>%
#  pivot_wider(
#    names_from = room_type,
#    values_from = med_price
#    )
```

```{r}
nyc_airbnb %>%
  filter(neighbourhood_group == "Staten Island", room_type == "Shared room") %>% view
```

```{r}
nyc_airbnb %>%
  group_by(neighbourhood_group, neighbourhood) %>%
  summarize(
    mean_price = mean(price, na.rm = TRUE), 
    mean_review = mean(review_scores_location, na.rm = TRUE)
  ) %>%
  ggplot(aes(x = mean_review, y = mean_price)) + 
  geom_point() + 
  facet_grid(~neighbourhood_group)
```

```{r}
nyc_airbnb %>%
  count(neighbourhood)
```

```{r}
nyc_airbnb %>%
  filter(neighbourhood == "Astoria") %>%
  ggplot(aes(x = review_scores_location, y = price)) + 
  geom_point() 
```

## spatial locations

```{r}
nyc_airbnb %>% 
  filter(
    neighbourhood_group == "Manhattan",
    price > 1000) %>%
  ggplot(aes(x = lat, y = long, color = price)) +
  geom_point(alpha = .3)
```

